A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-05-15 paper/paper1/ms.tex
Placeholder for hydrodynamic simulation text

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/reinflation_MIST.png}
    \caption{Conceivable evolutionary scenarios for \hatpb.  The planet's equilibrium temperature increases as the stellar luminosity gradually increases on the main sequence.  The Ohmic dissipation model makes predictions for runaway inflation, depending on the incident stellar flux.  The heuristic scaling relation for the inflation timescale predicts unusually small values in this extreme regime but illustrates the countervailing effects of the top two panels.}
    \label{fig:OhmicInflate}
\end{figure}

>>>>

\subsection{3D Hydrodynamic simulations}
\authorcomment1{Insert Morgan Macleod text here.}
\textcolor{lightgray}{Habitasse platea dictumst vestibulum rhoncus est pellentesque elit ullamcorper dignissim. Odio ut sem nulla pharetra. Odio ut sem nulla pharetra diam sit amet nisl suscipit. Accumsan tortor posuere ac ut. Ornare arcu dui vivamus arcu felis bibendum ut tristique. Nunc faucibus a pellentesque sit amet porttitor eget. Mauris rhoncus aenean vel elit. Sed vulputate mi sit amet mauris commodo. Quis lectus nulla at volutpat diam ut venenatis. Sed id semper risus in hendrerit gravida rutrum quisque non. Est placerat in egestas erat imperdiet sed. Viverra adipiscing at in tellus integer feugiat scelerisque varius. Quam viverra orci sagittis eu volutpat odio facilisis mauris sit. Morbi tristique senectus et netus et malesuada. Duis tristique sollicitudin nibh sit amet. Libero nunc consequat interdum varius sit amet mattis vulputate. Velit ut tortor pretium viverra suspendisse potenti nullam ac. Viverra accumsan in nisl nisi scelerisque eu ultrices vitae. Quis commodo odio aenean sed adipiscing diam donec.}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/reinflation_MIST.png}
    \caption{Conceivable evolutionary scenarios for \hatpb.  The planet's equilibrium temperature increases as the stellar luminosity gradually increases on the main sequence.  The second panel from top shows the corresponding estimate for anomalous heating efficiency from \citet{2018AJ....155..214T}. The Ohmic dissipation model makes predictions for runaway inflation, depending on the incident stellar flux.  The heuristic scaling relation for the inflation timescale predicts vanishingly short inflationary lifetimes in this extreme regime but illustrates the countervailing effects of the top two panels.}
    \label{fig:OhmicInflate}
\end{figure}
